\section{Referencias y Recursos}

\begin{thebibliography}{9}

\bibitem{wireguard}
Donenfeld, J. A. (2017). 
\textit{WireGuard: Next Generation Kernel Network Tunnel}. 
NDSS 2017. Network and Distributed System Security Symposium.

\bibitem{docker}
Docker Inc. (2025). 
\textit{Docker Documentation - Networking}. 
Disponible en: \url{https://docs.docker.com/network/}

\bibitem{qos-rfc}
Nichols, K., Blake, S., Baker, F., \& Black, D. (1998). 
\textit{Definition of the Differentiated Services Field (DS Field) in the IPv4 and IPv6 Headers}. 
RFC 2474.

\bibitem{tc-howto}
Hubert, B., Graf, T., Maxwell, G., van Mook, R., van Oosterhout, M., Schroeder, P., \& Spaans, J. (2002). 
\textit{Linux Advanced Routing \& Traffic Control HOWTO}. 
Disponible en: \url{https://lartc.org/}

\bibitem{iptables}
Welte, H., \& Kadlecsik, J. (2025). 
\textit{netfilter/iptables project documentation}. 
Disponible en: \url{https://netfilter.org/}

\bibitem{docker-compose}
Docker Inc. (2025). 
\textit{Docker Compose Overview}. 
Disponible en: \url{https://docs.docker.com/compose/}

\bibitem{namespace}
Biederman, E. W. (2006). 
\textit{Multiple instances of the global Linux namespaces}. 
Proceedings of the Linux Symposium, Vol. 1, pp. 101-112.

\bibitem{vpn-security}
Oppliger, R. (2003). 
\textit{Internet and Intranet Security}. 
Artech House, Segunda Edición.

\bibitem{qos-networking}
Ferguson, P., \& Huston, G. (1998). 
\textit{Quality of Service: Delivering QoS on the Internet and in Corporate Networks}. 
John Wiley \& Sons.

\end{thebibliography}
